---
title: "Coalition Management in Brazil"
subtitle: "A dataset"
author: Frederico Bertholini
output: ioslides_presentation:
       logo: logo.jpeg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval=F)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

# Como usar

## Baixando dados do dataverse

- Wide (mês/ano)
```{r }
# Reading data from dataverse
data <- get_file("parties_brazil_long.RDS", "doi:10.7910/DVN/9EJGE9")
CMV8 <- tempfile(fileext = ".RDS")
writeBin(as.vector(data), CMV8)
CMV8_longs <- readRDS(CMV8) 
```

- Longe (partido/mês/ano)
```{r}
# Reading data from dataverse
data <- dataverse::get_file("parties_brazil_long.xlsx", "doi:10.7910/DVN/9EJGE9")
df_wide <- tempfile(fileext = ".xlsx")
writeBin(as.vector(data), df_wide)
CMV8_longs <- readxl::read_xlsx(CMV8) 
```

## Pronto, 


